---
title: "Facebook Data Analysis"
author: 'Ahnaf Ryan: 20757532'
date: "February 16, 2021"
output:
  pdf_document: default
  html: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Case Study
This is a case study about the effectiveness of various posts of a cosmetics company facebook's page.

##Importing the Data
```{r}
fb<-read.csv('facebook.csv')
head(fb)
```


## What is the typical number of likes from a facebook post?
We are interested in the measure of location and the word "typical" may suggest to look for mean , median or mode. However, it is common knowledge to think that more views of a post will likely increase the number of likes, hence we need to weight the post based on the impressions.

```{r}
subdata<-na.omit(fb)
plot(subdata$Impressions,subdata$like,ylab="Number of Likes",xlab="Impressions",
     main="Scatter plot of Impressions and likes")
```

From the scatter plot, it is difficult to understand the relationship between Number of Likes and Impressions. To have a better understanding, let us apply power transformation to the variates.
```{r}
library("MASS")
powerfun<-function(x,alpha) {
  if(sum(x<=0) > 0) stop("x must be positive")
  if (alpha==0)
    log(x)
  else if (alpha>0) {
    x^alpha
  }
  else -x^alpha
}
rho_cor<-function(alpha,x,y) {
  alphax<-alpha[1]
  alphay<-alpha[2]
  return(-abs(cor(x=powerfun(x,alphax),y=powerfun(y,alphay))))
}
min3<-nlminb(start=c(1,1),objective = rho_cor,y=subdata$like+1,x=subdata$Impressions)
print(min3)
new_y<-(subdata$like +1)^(min3$par[2])
new_x<-(subdata$Impressions)^(min3$par[1])
plot(new_x,new_y,main="transformed data")
abline(lm(new_y~new_x))
```
We optimize the correlation function and choose the best power parameters of our variates. After applying the transformation, we see they have a expotential relationship which is a interesting observation because we can confirm that there is a relation between number of likes and expressions and we know their structure based on the dataset.




To find the "typical" number of likes, we used a robust mean estimator known "Tukey's Biweight". We see the "typical" number of likes is 111 likes per post.
```{r}
library("DescTools")
TukeyBiweight(subdata$like)
```
We want to test the hypothesis whether the investment made into facebook advertisement has impacted the number of likes of a post for a particular category. The reason to test this hypothesis is that if there is not statistical significance between paid and unpaid, then we can redistribute our investment into categories that are affected or statistically significant.From the aggregate, it seems like category "inspiration", the values did not change significantly. For the category "inspiration", We define $H_o= \mu_(unpaid)=\mu_(paid)$.We find that the p-value is 0.21466556 hence there is no evidence against the null hypothesis based on the observed data. These proves that based on the observed,the investment for the category "inspiration" has no effect on the number of likes. Hence we allocate this investment into the other categories for effective investment.

```{r}
head(subdata)
paid_data<-subdata[subdata$Paid==1,]
unpaid_data<-subdata[subdata$Paid==0,]
TukeyBiweight(paid_data$like)
setNames(aggregate(x=paid_data$like,by=list(paid_data$Category),FUN=mean),c("Categories","Likes"))
setNames(aggregate(x=unpaid_data$like,by=list(unpaid_data$Category),FUN=mean),c("Categories","Likes"))
proportion_paid<-length(which(paid_data$Category=="Inspiration"))/139
proportion_unpaid<-length(which(unpaid_data$Category=="Inspiration"))/495
ins_paid_data<-paid_data[paid_data$Category=="Inspiration",]
ins_unpaid_data<-unpaid_data[unpaid_data$Category=="Inspiration",]
v1<-(1/(nrow(ins_unpaid_data)-1))*var(ins_unpaid_data$like)
v2<-(1/(nrow(ins_paid_data)-1))*var(ins_paid_data$like)
d=(mean(ins_paid_data$like)-mean(ins_unpaid_data$like))/sqrt((v1/nrow(ins_unpaid_data))+(v2/nrow(ins_paid_data)))
1-pt(d,df=nrow(ins_paid_data)+nrow(ins_unpaid_data)-2)
```
We can see 30 percent of the paid advertisements were directed to inspirational categories which seems a waste of advertisement money in terms of number of likes.
```{r}
aggregate(x=paid_data$Impressions,by=list(paid_data$Category),FUN=mean)
aggregate(x=unpaid_data$Impressions,by=list(unpaid_data$Category),FUN=mean)
length(which(paid_data$Category=="Inspiration"))/139
length(which(unpaid_data$Category=="Inspiration"))/495
```
Let us now perform the hypothesis  whether the investment made into facebook advertisement has impacted the impression for a particular category.
```{r}
setNames(aggregate(x=paid_data$like,by=list(paid_data$Type),FUN=mean),c("Categories","Likes"))
setNames(aggregate(x=unpaid_data$like,by=list(unpaid_data$Type),FUN=mean),c("Categories","Likes"))
length(which(paid_data$Type=="Link"))/139
length(which(unpaid_data$Type=="Link"))/495
```